---
title: "CaDrA's Rest API"
output: BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{CaDrA's Rest API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, messages=FALSE, warnings=FALSE}
knitr::opts_chunk$set(message=FALSE, collapse = TRUE, comment="")
library(knitr)
library(httr)
library(jsonlite)
```

<script type="text/javascript">

  function ToggleOperation(id) {
    var x = document.getElementById(id+"-block");
    if (x.style.display === "none") {
      x.style.display = "block";
    } else {
      x.style.display = "none";
    }
  }

</script>

# CaDrA's Rest API

<p>Here we provide documentation on how to retrieve pre-processed dataset from our CaDrA web portal. All successful responses are returned in JSON. Only queries that respond with a 200 response code is considered successful.</p>

<p>Here are standard HTTP codes that you will find in the “Status” element of the response body.</p>

```{r status-table, include=TRUE, echo=TRUE, results='asis'}
```
<table class="status-table">
  <tr>
    <td><strong>Status Code</strong></td>
    <td><strong>Description</strong></td>
  </tr>
  <tr>
    <td>200 OK</td>
    <td>Standard HTTP successful response</td>
  </tr>
  <tr>
    <td>404 Bad Request or Source Not Found</td>
    <td>Standard HTTP invalid request response</td>
  </tr>
  <tr>
    <td>500 Internal Server Error</td>
    <td>There was an unexpected error on our server. If you see this error, please notify us about the issue on our <a target="blank" href="https://github.com/montilab/CaDrA.shiny/issues">GitHub page</a></td>
  </tr>
</table>

<br>

## API_Server: https://montilab.bu.edu/CaDrA_API

<br>

<p>There are four data sources that currently available from the API.</p>

```{r source-table, include=TRUE, echo=TRUE, results='asis'}
```
<table class="source-table">
  <tr>
    <td><strong>Data</strong></td>
    <td><strong>Description</strong></td>
    <td><strong>Return</strong></td>
  </tr>
  <tr>
    <td>get_feature_set</td>
    <td>a list of pre-proccessed feature sets available on CaDrA's web portal</td>
    <td>data frame</td>
  </tr>
  <tr>
    <td>get_input_score</td>
    <td>a list of input scores associated with a particular feature set available on CaDrA's web portal</td>
    <td>data frame</td>
  </tr>
  <tr>
    <td>get_gene_expression</td>
    <td>a gene expression set associated with a particular feature set available on CaDrA's web portal</td>
    <td>data frame</td>
  </tr>
  <tr>
    <td>download_feature_set</td>
    <td>a bundle of RDS files for a given feature set. Users also have the option to whether or not to include input scores and gene expression set that associated with that feature set.</td>
    <td>zip file</td>
  </tr> 
</table>

<br>

<!-- get_feature_set: start -->
### get_feature_set

<table class="get-table">
  <tr>
    <td><button type="button" onclick="ToggleOperation('get_feature_set')" class="btn btn-default action-button">GET</button></td>
    <td>&#47;get_feature_set</td>
    <td>Return a list of pre-proccessed feature sets available on CaDrA's web portal</td>
  </tr>
</table>

<div id="get_feature_set-block" style="display: none;">

<h4>Implementation</h4>

<p><a target="blank" href="https://montilab.bu.edu/CaDrA_API/get_feature_set">https://montilab.bu.edu/CaDrA_API/get_feature_set</a></p>

<h4>Return</h4>

<p>A data frame with two columns: description and feature_set_name</p>

<br>

<h4>Example in R</h4>

```{r}

# url for local testing
url0 <- "https://montilab.bu.edu/CaDrA_API/get_feature_set"

# Send GET Request to API
res <- GET(url = url0, encode = "json")

# Check the status of GET request 
test_request <- tryCatch({
  
  stop_for_status(res)
  
  "pass"
  
}, error = function(e) {
  
  "fail"
  
})

```

<h4>Output</h4>

```{r}

# If GET request is successful, return the results
if(test_request == "pass"){
  
  projects <- fromJSON(fromJSON(rawToChar(res$content)))
  knitr::kable(head(projects))
  
}
      
```

<br>

</div>

<!-- get_input_score: start -->
### get_input_score

<table class="get-table">
  <tr>
    <td><button type="button" onclick="ToggleOperation('get_input_score')" class="btn btn-default action-button">GET</button></td>
    <td>&#47;get_input_score</td>
    <td>Return a list of input scores associated with a given feature set available on CaDrA's web portal</td>
  </tr>
</table>

<div id="get_input_score-block" style="display: none;">

<h4>Implementation</h4>

<p><a target="blank" href="https://montilab.bu.edu/CaDrA_API/https://montilab.bu.edu/CaDrA_API/get_input_score?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG">https://montilab.bu.edu/CaDrA_API/get_input_score?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG</a></p>

<br>

<table class="api-table">
  <tr>
    <td><strong>Parameter</strong></td>
    <td><strong>Description</strong></td>
    <td><strong>Data Type</strong></td>
  </tr>
  <tr>
    <td>feature_set</td>
    <td>a feature set name</td>
    <td>string</td>
  </tr>
</table>

<br>

<h4>Return</h4>

<p>A data frame with two columns: feature_set_name and input_score_name</p>

<br>

<h4>Example in R</h4>

```{r}

# url for local testing
url1 <- "https://montilab.bu.edu/CaDrA_API/get_input_score?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG"

# Send GET Request to API
res <- GET(url = url1, encode = "json")

# Check the status of GET request 
test_request <- tryCatch({
  
  stop_for_status(res)
  
  "pass"
  
}, error = function(e) {
  
  "fail"
  
})

```

<h4>Output</h4>

```{r}

# If GET request is successful, return the results
if(test_request == "pass"){
  
  projects <- fromJSON(fromJSON(rawToChar(res$content)))
  knitr::kable(head(projects))
  
}
      
```

<br>

</div>

<!-- get_gene_expression: start -->
### get_gene_expression

<table class="get-table">
  <tr>
    <td><button type="button" onclick="ToggleOperation('get_gene_expression')" class="btn btn-default action-button">GET</button></td>
    <td>&#47;get_gene_expression</td>
    <td>Return a gene expression set associated with a given feature set available on CaDrA's web portal</td>
  </tr>
</table>

<div id="get_gene_expression-block" style="display: none;">

<h4>Implementation</h4>

<p><a target="blank" href="https://montilab.bu.edu/CaDrA_API/get_gene_expression?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG">https://montilab.bu.edu/CaDrA_API/get_gene_expression?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG</a></p>

<br>

<table class="api-table">
  <tr>
    <td><strong>Parameter</strong></td>
    <td><strong>Description</strong></td>
    <td><strong>Data Type</strong></td>
  </tr>
  <tr>
    <td>feature_set</td>
    <td>a feature set name</td>
    <td>string</td>
  </tr>
</table>

<br>

<h4>Return</h4>

<p>A data frame with two columns: feature_set_name and gene_expression_name</p>

<br>

<h4>Example in R</h4>

```{r}

# url for local testing
url3 <- "https://montilab.bu.edu/CaDrA_API/get_gene_expression?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG"

# Send GET Request to API
res <- GET(url = url3, encode = "json")

# Check the status of GET request 
test_request <- tryCatch({
  
  stop_for_status(res)
  
  "pass"
  
}, error = function(e) {
  
  "fail"
  
})

```

<h4>Output</h4>

```{r}

# If GET request is successful, return the results
if(test_request == "pass"){
  
  projects <- fromJSON(fromJSON(rawToChar(res$content)))
  knitr::kable(head(projects))
  
}
      
```

<br>

</div>

<!-- download_feature_set: start -->
### download_feature_set

<table class="get-table">
  <tr>
    <td><button type="button" onclick="ToggleOperation('download_feature_set')" class="btn btn-default action-button">GET</button></td>
    <td>&#47;download_feature_set</td>
    <td>Return a zip file with a bundle of RDS files for a given feature set. Users also have the option to whether or not to include input scores and gene expression set that associated with that feature set.</td>
  </tr>
</table>

<div id="download_feature_set-block" style="display: none;">

<h4>Implementation</h4>

<p><a target="blank" href="https://montilab.bu.edu/CaDrA_API/download_feature_set?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG&include_input_score=TRUE&inclue_gene_expression=TRUE">https://montilab.bu.edu/CaDrA_API/download_feature_set?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG&include_input_score=TRUE&inclue_gene_expression=TRUE</a></p>

<br>

<table class="api-table">
  <tr>
    <td><strong>Parameter</strong></td>
    <td><strong>Description</strong></td>
    <td><strong>Data Type</strong></td>
  </tr>
  <tr>
    <td>feature_set</td>
    <td>a feature set name</td>
    <td>string</td>
  </tr>
  <tr>
    <td>include_input_score</td>
    <td>whether to include input score. Default is TRUE.</td>
    <td>string</td>
  </tr>
  <tr>
    <td>include_gene_expression</td>
    <td>whether to include gene expresion set. Default is TRUE.</td>
    <td>string</td>
  </tr>
</table>

<br>

<h4>Return</h4>

<p>A zip file</p>

<br>

<h4>Example in R</h4>

```{r}

# url for local testing
url4 <- "https://montilab.bu.edu/CaDrA_API/download_feature_set?feature_set=TCGA_ACC_2016_01_28_GISTIC_MUT_SIG&include_input_score=TRUE&inclue_gene_expression=TRUE"

```

<h4>Output</h4>

```{r}

out_dir <- tempdir()

file_dir = file.path(out_dir, paste0("download-fs-", Sys.Date()))

zip_file = paste0(file_dir, ".zip")

download.file(url4, zip_file)

file_list <- unzip(zip_file, exdir=out_dir, list=TRUE)

knitr::kable(head(file_list))

```

<br>

</div>



